---
title: "Introduction to Quantile Regression"
author: Anton Antonov
date: 2020-09-14
output: html_notebook
---

```{r, setup}
library(magrittr)
library(MathematicaVsRData)
library(quantreg)
library(QRMon)
```

# Introduction

In this notebook we are going to introduce Quantile Regression (QR) through questions and answers.

Each of the questions listed below is answered in separate section in this notebook.

*(This is non-computational notebook, but the code examples are expected to run.)*

# Basic questions 

1. What is the mission statement of the course?

2. Why use QR? 

   - What are the main advantages of using QR?
   
   - Is it just for better visualization of the signals?

3. How does QR compare to other related methods?

4. Can QR be used for forecast?

5. Can we use Neural Networks instead of QR?

6. Are there implementations in other popular "data science" programming languages?

7. Where can I find the theoretical background for QR computations?

## Addtional questions

I have accumulated a list of questions and comments from my Quantile Regression (QR) presentations. 

1. Can apply QR without the package QRMon?

   - Yes, see the Wolfram Functions Repository item "QuantileRegression".

   - Related, why are you using QRMon?

2. Are you computing QR using a moving window?

   - Related, how QR compares to Local regression?

3. What do you do when the QR fitted curves (regression quantiles) intersect? 

4. How does QR look like over 3 points?

5. What approximation to pick for reconstructing the conditional CDF's?


9. What is the point of using those anomaly detection methods -- a human can easily do it?



# Mission statement

The goals of this (workshop) lectures are to:

- Introduce the theoretical background of QR,

- Demonstrate QR's practical (and superior) abilities to deal with "real life" time series data

- Teach how to rapidly create QR workflows using R


# Why use QR?

# Can QR be used for forecast?


# How does QR look like over 3 points?

```{r}
res <- 
  QRMonUnit( runif(n = 4, min = 1, max = 10) ) %>% 
  QRMonQuantileRegression( df = 2, probabilities = 0.5, degree = 2 ) %>% 
  QRMonPlot
```

# References

TBD...