---
title: "Quantile Regression packages"
author: Anton Antonov
date: 2020-09-14
output: html_notebook
---

# Introduction

In this notebook we show how to install the R packages used in this QR course and how to verify they are working.

The QR packages used in the course are `quantreg` and `QRMon`.

# Packages installation

**1.** Install `devtools` (if you have not already.)

```{r, eval=FALSE}
install.packages("devtools")
```


**2.** Install `quantreg`:

```{r, eval=FALSE}
install.packages("quantreg")
```

**3.** Install `QRMon-R`:

```{r, eval=FALSE}
#install.packages("devtools")
devtools::install_github(repo = "antononcube/QRMon-R" )
```

**4.** Install the data package [`MathematicaVsRData`](https://github.com/antononcube/R-packages/tree/master/MathematicaVsRData):

```{r, eval=FALSE}
devtools::install_github(repo = "antononcube/R-packages", subdir = "MathematicaVsRData" )
```

# Verifications

## `quantreg`

```{r}
library(quantreg)
```


```{r}
data(engel)
fit1 <- rq(foodexp ~ income, tau = .5, data = engel)
```

```{r}
summary(fit1)
```

## `QRMon`

```{r}
library(magrittr)
library(QRMon)
```

The package `QRMon` has its own data; here we use `dfTemperatureData`:

```{r}
res <- 
  QRMonUnit( dfTemperatureData ) %>% 
  QRMonQuantileRegression( df = 12 ) %>% 
  QRMonPlot(datePlotQ = T, dateOrigin = "1900-01-01")
```

# Vignettes

## `quantreg`

Here is how to get the vignette for `quantreg` written by package's author [Roger Koenker](https://en.wikipedia.org/wiki/Roger_Koenker):

```{r, eval=FALSE}
vignette("rq", package= "quantreg")
```

Alternatively:

- Read its online version: 
["Quantile Regression in R: a Vignette"](https://cran.r-project.org/web/packages/quantreg/vignettes/rq.pdf).

- Read another version that might be of interest:
["Censored Quantile Regression Redux"](https://cran.r-project.org/web/packages/quantreg/vignettes/crq.pdf).


## `QRMon`

Here is how to the vignette for `QRMon`:

```{r}
vignette("rq", package= "QRMon")
```

Or read its online version:
["Rapid making of Quantile Regression workflows"](https://htmlpreview.github.io/?https://github.com/antononcube/QRMon-R/blob/master/notebooks/rapid-making-of-qr-workflows.html).